\chapter{Introduction}
Many people are using slideshows, in various forms, at a daily basis. There are a lot of different methods for creating a slideshow; there are programs that make it possible for the user to create slideshows relatively simple, and there are programming languages that are designed for the purpose of creating a slideshow. The software solutions for creating slideshows that will be discussed briefly are; Apple Keynote, Microsoft Office PowerPoint, \LaTeX~Beamer and NISSE (Nearly Instantaneous Slide Show Expressions). \\
A similarity that Keynote and PowerPoint have in common is that they are both pointing device based slideshow programs, which means that without using a pointing device you cannot use them properly, whereas \LaTeX~Beamer is not pointing device dependent. With \LaTeX~Beamer not being a pointing device dependent slideshow programming language makes the direct rival to the NISSE language.
A functionality that \LaTeX~Beamer lacks out on is that option for the user to use it properly at a mobile device. With “properly’’ is meant that you can use it mobile, but Latex is a complex programming languages with a lot of packages, and the \LaTeX~Beamer class can use the same packages as Latex, which makes it complex to remember which packages that gives the user the exact functionality that we want. As an example of the use of packages to gain certain functionality could be that if the user wants to make a sections of his slide a certain colour, e.g. red, he has to include \usepackage{color} to make this possible. A goal with NISSE is to create a slideshow programming language where the user does not have to remember a lot of different packages to give certain functionality, or have to google how to get able to the some specific functionality. When the user has finished creating the slideshow, or if he wants to compile it, he can send it to a server that automatically compiles the slideshow for him and returns the compiled slideshow in an .HTML or .PDF-file, makes the user able to see the slideshow.\\


%\section{Server Compiler}
%A way to make the language easier to compile is to take the workload off the user's computer, and place it on a server. This creates the aspect that you can write and compile code anywhere, on any computer, or mobile device\footnote{A mobile device is defined as a laptop, tablet, smartphone, etc.}, with internet access without any additional programs.
%Having the compilation phase on a server creates the possibility to write the slideshow\footnote{The slideshow is being compiled in to one single HTML-file} on a cellphone, which can send the code to the server and receive the presentation on the device.
%With the Internet getting faster and faster\textbf{KILDE!}, more users are online, which does not limit the possibility for the users to compile their slideshows, although the compiler can be downloaded for offline use if needed.\\
\\ \\
After a walkthrough of the system, there will be a conclusion to summarize the report in general. Following this the further development section presents ideas and functionalities which could or should be implemented in the system. Included with the report is a CD containing the developed system, the source code of the developed system and the report.